---
title: "Bootstrap"
format: html
editor: 
  markdown: 
    wrap: sentence
---

```{r}
library(tidyverse)
library(boot)
library(lmboot)
```

```{r}
books <- read.csv("outputs\\books_cleaned_for_analysis.csv")
```

Bootstrap methods provide robust inference for coefficient estimation and prediction.
We will:

1\.
Draw at least 1,000 bootstrap samples with replacement.

2\.
Refit the regression model on each sample to obtain empirical coefficient distributions.

3\.
Construct percentile and BCa bootstrap confidence intervals.

4\.
Perform a residual bootstrap to generate predictive intervals for ratings.

5\.
Compute empirical p-values for hypotheses such as:

```{r}
mdl <- lm(average_rating ~ num_pages + pages_squared + 
                   log_ratings_count + log_text_reviews + genre_category,
                 data = books)
summary(mdl)
```

```{r}
hist(books$num_pages)
hist(books$pages_squared)
hist(books$log_ratings_count)
hist(books$log_text_reviews)
```

```{r}
set.seed(100)


coef_function <- function(formula, data, indices) {
  d <- data[indices,] #allows boot to select sample
  fit <- lm(formula, data=d) #fit regression model
  return(coef(fit)) #return coefficient estimates of model
}


bootstraps <- boot(data=books, statistic=coef_function, R=1000, formula=average_rating ~ num_pages + pages_squared + 
                   log_ratings_count + log_text_reviews + genre_category)


```

```{r}
bootstraps
```

```{r}
#histograms of bootstrap sample coefficients
hist(bootstraps$data$num_pages)
hist(bootstraps$data$pages_squared)
hist(bootstraps$data$log_ratings_count)
hist(bootstraps$data$log_text_reviews)


```

```{r}
# residual bootstrap!

resboot <- residual.boot(average_rating ~ num_pages + pages_squared + 
                   log_ratings_count + log_text_reviews + genre_category, B = 1000, data = books, seed = 100)


hist(resboot$bootEstParam[,2], main="Residual Bootstrap Sampling Distn.",
     xlab="num_pages Slope Estimate") 

hist(resboot$bootEstParam[,3], main="Residual Bootstrap Sampling Distn.",
     xlab="pages_squared Slope Estimate")

quantile(resboot$bootEstParam[,2], probs=c(.025, .975)) #num_pages

```
